% !TEX root = ../../thesis.tex

\section{Regularity}\label{sec:regularity}

By Proposition~\ref{thm:CLS-stationary}, the limit varifold $V$ is stationary; by Theorem~\ref{thm:integrality}, $V$ is integral. In the no-mass-cancellation case, $V = |\partial^*\Omega(x_0)|$ is a stationary integral varifold of multiplicity one; Allard regularity~\cite[Theorem~24.2]{Sim84} then directly yields a smooth embedded minimal hypersurface. The mass-cancellation case requires more work: we apply Wickramasekera's regularity theorem (Theorem~\ref{thm:wickramasekera}), which requires two further inputs---\emph{stability} and the \emph{$\alpha$-structural hypothesis} (Definition~\ref{defn:alpha-structural}). This section verifies both.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Stability}\label{subsec:stability}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

The non-excessive condition provides stability through the following chain of implications: non-excessiveness ensures that the limit varifold $V$ is one-sided homotopic minimizing at all but finitely many points, and one-sided minimization implies stability.

\begin{proposition}[Stability of the limit varifold]\label{prop:stability}
Let $\Phi$ be a non-excessive ONVP sweepout, $x_i \to x_0 \in \mathfrak{m}(\Phi)$ a min-max sequence, and $V$ the varifold limit of $|\partial^*\Omega(x_i)|$. Then $V$ is stable.
\end{proposition}

\begin{proof}
By~\cite[Proposition~3.1]{CLS22}, the set $\mathfrak{h}_{\mathrm{nm}}(V)$ of non-homotopic-minimizing points (Definition~\ref{def:hnm}) is finite. Therefore $V$ is one-sided homotopic minimizing in $B_r(P)$ for every $P \in \spt\|V\| \setminus \mathfrak{h}_{\mathrm{nm}}(V)$ and some $r = r(P) > 0$. One-sided homotopic minimization implies that the second variation $\delta^2 V(\varphi, \varphi) \geq 0$ for all normal deformations $\varphi$ supported in $B_r(P)$. Since the finitely many points of $\mathfrak{h}_{\mathrm{nm}}(V)$ form a set of $\mathcal{H}^n$-measure zero, a partition-of-unity argument extends stability to all compactly supported normal deformations, giving global stability.

We remark that the finiteness of $\mathfrak{h}_{\mathrm{nm}}(V)$ in~\cite[Proposition~3.1]{CLS22} relies on both the non-excessive property and the nestedness of the sweepout: the proof constructs replacement families by ``gluing in'' one-sided homotopies, and nestedness ($\Omega(x_1) \subset \Omega(x_2)$) ensures that the parameter sets on which these replacements are defined are intervals. This is the only place in our regularity argument where nestedness is used (see Remark~\ref{rem:integrality-independence}). We also note that~\cite[Proposition~3.1]{CLS22} does not require the identification $V = |\partial^*\Omega(x_0)|$; in particular, the argument applies equally in the mass-cancellation case.
\end{proof}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{The $\alpha$-structural hypothesis}\label{subsec:alpha-structural}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

We first show that the fold case ($N = 2$) cannot arise at a genuine singular point, so any failure of the $\alpha$-structural hypothesis produces a wedge with angle $< \pi$.

\begin{lemma}[Wedge at singular junctions]\label{lem:wedge}
Let $V$ be a stable stationary integral $n$-varifold in $(M^{n+1}, g)$ and $Z \in \sing V$ a point at which the $\alpha$-structural hypothesis \textup{(}Definition~\textup{\ref{defn:alpha-structural})} fails. Then any tangent cone $C$ of $V$ at $Z$ consists of $N \geq 3$ half-hyperplanes $P_1^+, \ldots, P_N^+$ meeting along a common $(n-1)$-dimensional edge $L$. In particular, there exist two adjacent half-hyperplanes meeting at angle $\theta < \pi$.
\end{lemma}

\begin{proof}
Since the $\alpha$-structural hypothesis fails at $Z$, there exists $\rho > 0$ such that $\spt\|V\| \cap B_\rho(Z)$ consists of finitely many $C^{1,\alpha}$ embedded hypersurfaces-with-boundary meeting along a common $C^{1,\alpha}$ boundary $\Gamma$ of dimension $n - 1$. Blowing up at $Z$, any tangent cone $C$ is a stationary integral cone consisting of $N$ half-hyperplanes $P_1^+, \ldots, P_N^+$ meeting along a common edge $L$, each carrying a positive integer multiplicity $m_j$, with the stationarity balance $\sum_{j=1}^N m_j \nu_j = 0$ (where $\nu_j$ is the outward unit normal to $P_j^+$ in the $2$-plane perpendicular to $L$).

We claim $N \geq 3$. By~\cite[Remark~(3) following~($\mathcal{S}3$)]{Wic14}, for stable codimension~$1$ integral varifolds, the $\alpha$-structural hypothesis~($\mathcal{S}3$) is equivalent to the condition that no tangent cone at a singular point is supported by three or more distinct half-hyperplanes meeting along a common $(n-1)$-dimensional subspace. In particular, $N = 2$ does not constitute a failure of~($\mathcal{S}3$): when the tangent cone is a flat hyperplane (possibly with multiplicity $\geq 2$), the Sheeting Theorem~\cite[Theorem~3.3]{Wic14} ensures regularity. Therefore $N \geq 3$, and the $N$ half-hyperplanes partition the $2$-plane perpendicular to $L$ into $N$ sectors with angles $\theta_1, \ldots, \theta_N$ summing to $2\pi$. By the pigeonhole principle, $\min_j \theta_j \leq 2\pi/N < \pi$.
\end{proof}

\begin{theorem}[Verification of $\alpha$-structural hypothesis]\label{thm:alpha-hypo}
    Let $V$ be the stationary integral varifold arising from a non-excessive ONVP sweepout $\Phi$
    with width $W$, via the min-max sequence $x_i \to x_0 \in \mathfrak{m}(\Phi)$. Then $V$ satisfies the $\alpha$-structural hypothesis (Definition~\ref{defn:alpha-structural}).
\end{theorem}

\begin{remark}\label{rem:junction-cases}
Theorem~\ref{thm:alpha-hypo} is only invoked in the mass-cancellation case (see the proof of Theorem~\ref{thm:non-excessive-main} below): when no mass cancellation occurs, $V = |\partial^*\Omega(x_0)|$ is a stationary varifold of multiplicity one, hence smooth by Allard regularity, so $\sing V = \varnothing$ and the $\alpha$-structural hypothesis is vacuously satisfied.
\end{remark}

\begin{proof}
Suppose the $\alpha$-structural hypothesis fails at some $Z \in \sing V$. By Lemma~\ref{lem:wedge}, the tangent cone at $Z$ contains two adjacent half-hyperplanes $P_j^+, P_{j+1}^+$ meeting at angle $\theta_j < \pi$ along a common $(n-1)$-dimensional edge $L$.

\medskip\noindent\textbf{Step~1: Chord-beats-arc on the tangent cone.}
In each two-dimensional cross-section normal to $L$, the two half-lines $P_j^+ \cap \partial B_r$ and $P_{j+1}^+ \cap \partial B_r$ have total length $2r$, while the chord connecting their endpoints has length $2r\sin(\theta_j/2) < 2r$ (see Figure~\ref{fig:chord-beats-arc}). Integrating along $L$, the replacement surface has strictly less area:
\[
    \|C\|(B_r) - \|\widetilde{C}\|(B_r) \geq \delta(\theta_j) \cdot r^n > 0.
\]

    \begin{figure}[ht]
        \centering
        \begin{tikzpicture}[scale=1.0]
          % Edge L: shared edge of the two parallelograms, with perspective
          \coordinate (A) at (-1.8,-0.6);   % near end of edge
          \coordinate (B) at (1.8,0.6);     % far end of edge

          % H_1 (upper half-plane): parallelogram above L
          \coordinate (A1) at ($(A)+(1.2,2.4)$);
          \coordinate (B1) at ($(B)+(1.2,2.4)$);

          % H_2 (lower half-plane): parallelogram below L
          \coordinate (A2) at ($(A)+(2.4,-1.2)$);
          \coordinate (B2) at ($(B)+(2.4,-1.2)$);

          % Fill both half-planes
          \fill[fillA, opacity=0.35] (A) -- (B) -- (B1) -- (A1) -- cycle;
          \fill[fillA, opacity=0.35] (A) -- (B) -- (B2) -- (A2) -- cycle;

          % Draw H_1 edges
          \draw[thick, bindA] (A) -- (A1);
          \draw[thick, bindA] (B) -- (B1);
          \draw[bindA] (A1) -- (B1);

          % Draw H_2 edges
          \draw[thick, bindA] (A) -- (A2);
          \draw[thick, bindA] (B) -- (B2);
          \draw[bindA] (A2) -- (B2);

          % Edge L (drawn on top)
          \draw[very thick] (A) -- (B);

          % Midpoint of L and ball B_r
          \coordinate (M) at ($(A)!0.5!(B)$);
          % Circle split at tangent points: short arc (right) solid, long arc (left) dashed
          \draw[gray, thin] ($(M)+(-18:1.2)$) arc[start angle=-18, end angle=55, radius=1.2];
          \draw[gray, thin, dashed] ($(M)+(55:1.2)$) arc[start angle=55, end angle=342, radius=1.2];
          \fill[gray] (M) circle (1.5pt);
          \node[gray, above left] at ($(M)+(135:1.2)$) {$\partial B_r$};

          % Two points on L inside the circle, on either side of M
          \coordinate (P) at ($(A)!0.35!(B)$);
          \coordinate (Q) at ($(A)!0.65!(B)$);
          \fill (P) circle (1.5pt);
          \fill (Q) circle (1.5pt);

          % Blue gradient shading for chord competitor (between semi-ellipses and chord)
          \shade[left color=blue!30, right color=blue!5, shading angle=18, opacity=0.5]
            (P) .. controls (-0.11, 0.69) and (0.50, 1.14) .. (0.69, 0.99)
            -- (1.14, -0.37)
            .. controls (1.08, -0.61) and (0.33, -0.61) .. cycle;

          % Gray shading for the wedge region (between chord and arc)
          \fill[gray, opacity=0.25]
            (0.69, 0.99) -- (1.14, -0.37)
            arc[start angle=-18, end angle=55, radius=1.2]
            -- cycle;

          % Semi-ellipse on H_1 side: solid left part, dashed right part
          \draw[thick] (P) .. controls (-0.11, 0.69) and (0.50, 1.14) .. (0.69, 0.99);
          \draw[thin, dashed] (0.69, 0.99) .. controls (0.79, 0.91) and (0.77, 0.65) .. (Q);

          % Semi-ellipse on H_2 side: solid left part, dashed right part
          \draw[thick] (P) .. controls (0.33, -0.61) and (1.08, -0.61) .. (1.14, -0.37);
          \draw[thin, dashed] (1.14, -0.37) .. controls (1.18, -0.25) and (1.01, -0.05) .. (Q);

          % Chord competitor: sparse parallel blue lines clipped to competitor region
          \begin{scope}
            \clip (P) .. controls (-0.11, 0.69) and (0.50, 1.14) .. (0.69, 0.99)
              -- (1.14, -0.37)
              .. controls (1.08, -0.61) and (0.33, -0.61) .. cycle;
            \foreach \s in {-0.15, 0.1, 0.35, 0.6} {
              \draw[blue, thin] ({\s-0.9}, {\s/3+2.72}) -- ({\s+0.9}, {\s/3-2.72});
            }
          \end{scope}

          % Rightmost solid blue line: shifted slightly right of T1-T2 to cover dashed ellipses
          \draw[blue, thin] (0.72, 0.97) -- (1.16, -0.37);

          % Past tangent points: dense dashed blue lines in the wedge region
          \begin{scope}
            \clip ($(M)+(-18:1.2)$)
              arc[start angle=-18, end angle=55, radius=1.2]
              .. controls (0.79, 0.91) and (0.77, 0.65) .. (Q)
              .. controls (1.01, -0.05) and (1.18, -0.25) .. cycle;
            \foreach \s in {-0.45,-0.35,...,0.85} {
              \draw[blue, thin, dashed] ({\s-0.9}, {\s/3+2.72}) -- ({\s+0.9}, {\s/3-2.72});
            }
          \end{scope}

          % Angle arc at far end B (interior angle, the Omega_C side)
          \draw[thin] (B) ++(-27:0.7) arc[start angle=-27, end angle=63, radius=0.7];
          \node at ($(B)+(18:1.0)$) {$\theta_j$};

          % Labels
          \node[bindA, above left] at ($(A1)!0.5!(B1)$) {$P_j^+$};
          \node[bindA, below right] at ($(A2)!0.5!(B2)$) {$P_{j+1}^+$};
          \node[above left] at ($(A)!0.3!(B)$) {$L$};
        \end{tikzpicture}
        \caption{Chord-beats-arc: two adjacent half-hyperplanes $P_j^+, P_{j+1}^+$ meet along the $(n-1)$-dimensional edge $L$ at angle $\theta_j < \pi$ (given by Lemma~\ref{lem:wedge}). In each $2$-dimensional cross-section normal to $L$, the two half-lines (solid arcs on the shaded half-planes) have total length $2r$, while the chord (blue hatched surface) has length $2r\sin(\theta_j/2) < 2r$. The grey region is the area saved by the replacement.}
        \label{fig:chord-beats-arc}
    \end{figure}

\medskip\noindent\textbf{Step~2: Transfer to $B_r(Z)$ and the approximating sequence.}
We transfer the cone-level area deficit to the approximating Caccioppoli sets. Choose normal coordinates centered at $Z$ so that $g_{ij}(Z) = \delta_{ij}$; then $g_{ij} = \delta_{ij} + O(r)$ in $B_r(Z)$. Since the $\alpha$-structural hypothesis fails at~$Z$, the $C^{1,\alpha}$ branches of $\spt\|V\|$ in $B_\rho(Z)$ converge to the tangent cone under blow-up: at scale~$r$, each branch deviates from its limiting half-hyperplane by $O(r^{1+\alpha})$, and the angle between adjacent branches is $\theta_j + O(r^\alpha)$, which remains $< \pi$ for $r$ sufficiently small.

By varifold convergence $|\partial^*\Omega(x_i)| \to V$ and the sheet decomposition (Lemma~\ref{lem:sheet-decomposition}), for each $r \in (0, \rho)$ sufficiently small and all $i$ sufficiently large, the smooth boundary $\partial^*\Omega(x_i) \cap B_r(Z)$ decomposes into smooth sheets, each a nearly flat graph approximating one of the $C^{1,\alpha}$ branches of $\spt\|V\|$. In particular, two adjacent sheets approximate $P_j^+$ and $P_{j+1}^+$, meeting at angle $\theta_j + O(r^\alpha) < \pi$ in $B_r(Z)$.

\medskip\noindent\textbf{Step~3: Caccioppoli surgery and contradiction with width.}
We perform chord surgery on the approximating Caccioppoli sets. In $B_r(Z)$, the two smooth sheets of $\partial^*\Omega(x_i)$ corresponding to the narrowest adjacent pair bound a thin wedge-shaped region. Replace these two sheets inside $B_{r/2}(Z)$ by a smooth interpolation surface (the ``chord surface''), which spans the same boundary on $\partial B_{r/2}(Z)$ but cuts across the wedge. The area of the chord surface on the curved sheets differs from the flat case by $O(r^{n+\alpha})$ (from the $C^{1,\alpha}$ deviation of the sheets from half-planes and the $O(r)$ metric deviation), so the net area saving is
\[
    \mathrm{Per}(\Omega(x_i), B_r(Z)) - \mathrm{Per}(\Omega(x_i)_r, B_r(Z)) \geq \delta(\theta_j) r^n - O(r^{n+\alpha}) \geq \frac{\delta(\theta_j)}{2}\, r^n > 0
\]
for $r$ small and $i$ large, where $\Omega(x_i)_r$ is the modified Caccioppoli set and $\delta(\theta_j) > 0$ depends only on $\theta_j$ and $n$. The surgery is localized in $B_r(Z)$, so $\mathrm{Per}(\Omega(x_i)_r) \leq \mathrm{Per}(\Omega(x_i)) - \delta(\theta_j) r^n / 2$.

Fix such an $r$. Since the $\alpha$-structural hypothesis fails at $Z \in \sing V$ and the junction structure is a property of $V$ (not of the approximating sequence), the same surgery applies to any slice $\Omega(x)$ with $x$ near $x_0$ and $\mathbf{M}(\partial^*\Omega(x))$ close to $W$: varifold convergence holds along any such sequence, producing the same near-junction sheets in $B_r(Z)$. Since $x_i \to x_0 \in \mathfrak{m}(\Phi)$ and $\mathrm{Per}(\Omega(x_i)) \to W$, the surgery produces a modified sweepout $\tilde{\Phi}$ that agrees with $\Phi$ outside a neighborhood of $x_0$ and satisfies
\[
    \sup_x \mathrm{Per}(\tilde{\Omega}(x)) < W.
\]
But $W = \inf_{\Psi} \sup_x \mathrm{Per}(\Psi(x))$ is the min-max width, a contradiction.

\medskip
Therefore, the $\alpha$-structural hypothesis holds.
\end{proof}

We can now assemble the full regularity result.

\begin{proof}[Proof of Theorem~\ref{thm:non-excessive-main}]
Let $(M^{n+1}, g)$ be a closed Riemannian manifold with $2 \leq n \leq 6$. By Theorem~\ref{thm:non-excessive-existence}, there exists a non-excessive ONVP sweepout $\Phi \in \Snm$. By Proposition~\ref{thm:CLS-stationary}, there exists a stationary varifold $V$ with $\mathbf{M}(V) = W$.

\medskip\noindent\emph{Case~1: no mass cancellation.}
By Theorem~\ref{thm:integrality-mult-one}, $V = |\partial^*\Omega(x_0)|$. Since $V$ is a stationary integral varifold of multiplicity one, Allard regularity~\cite[Theorem~24.2]{Sim84} gives that $\spt\|V\| = \partial^*\Omega(x_0)$ is a smooth, closed, embedded minimal hypersurface of multiplicity one.

\medskip\noindent\emph{Case~2: mass cancellation.}
By Theorem~\ref{thm:integrality}, $V$ is an integral varifold. By Proposition~\ref{prop:stability}, $V$ is stable. By Theorem~\ref{thm:alpha-hypo}, $V$ satisfies the $\alpha$-structural hypothesis. Therefore, all hypotheses of Wickramasekera's theorem (Theorem~\ref{thm:wickramasekera}) are satisfied, and $\sing V = \varnothing$. Thus $\spt\|V\|$ is a smooth, closed, embedded minimal hypersurface in $M$.
\end{proof}
